Code used to generate paper results : PMD analysis

### 2023-11-02 Paper_code-Database_CT.Rmd
Small changes in analysis

```{r library, message = FALSE}
.libPaths("/storage/research/dduv/cbio-lg/rlib/Bioc318/", include.site = FALSE)
library(readxl)
library(readr)
library(CTexploreR)
library(Vennerable)
library(biomaRt)
library(tidyverse)
library(SummarizedExperiment)
library(UpSetR)
library(ComplexHeatmap)
library(circlize)
library(SingleCellExperiment)
library(org.Hs.eg.db)
library(clusterProfiler)
library(msigdbr)
library(DOSE)
library(BiocParallel)
library(patchwork)
library(Biostrings)
```

@@

@@

```{r GO_ORA_meth}

go_ora_meth <- enrichGO(gene = 
                          filter(CT_genes, regulated_by_methylation)$ensembl_gene_id,
                        keyType = "ENSEMBL",
                        OrgDb = org.Hs.eg.db,
                        ont = "all",
                        readable = TRUE)
go_ora_meth <- simplify(go_ora_meth)

@@

go_ora_not_meth <- simplify(go_ora_not_meth)

>>>>

```{r library, message = FALSE}
library(readxl)
library(readr)
library(CTexploreR)
library(Vennerable)
library(biomaRt)
library(tidyverse)
library(SummarizedExperiment)
library(UpSetR)
library(ComplexHeatmap)
library(circlize)
library(SingleCellExperiment)
library(org.Hs.eg.db)
library(clusterProfiler)
library(msigdbr)
library(DOSE)
library(BiocParallel)
library(patchwork)
library(Biostrings)
```

@@

What about new genes in CTexploreR

```{r}
new <- CT_genes %>% 
  filter(!external_gene_name%in%common) %>% 
  pull(external_gene_name)

length(new)

# Charles' idea
# TCGA_expression(tumor = "all", genes = new, units = "log_TPM")
```

@@

```{r GO_ORA_meth}
go_ora_meth <- enrichGO(gene = 
                          filter(CT_genes, regulated_by_methylation)$ensembl_gene_id,
                        keyType = "ENSEMBL",
                        OrgDb = org.Hs.eg.db,
                        ont = "all",
                        readable = TRUE)
go_ora_meth <- simplify(go_ora_meth)

@@

go_ora_not_meth <- simplify(go_ora_not_meth)
as_tibble(go_ora_not_meth)

### 2023-11-02 Paper_code-PMD_analysis.Rmd
Small changes in analysis

```{r library, message = FALSE}
.libPaths("/storage/research/dduv/cbio-lg/rlib/Bioc318/", include.site = FALSE)
library(readr)
library(CTexploreR)
library(biomaRt)
library(tidyverse)
library(SummarizedExperiment)
library(BiocParallel)
library(patchwork)
library(Biostrings)
```

>>>>

```{r library, message = FALSE}
library(readr)
library(CTexploreR)
library(biomaRt)
library(tidyverse)
library(SummarizedExperiment)
library(BiocParallel)
library(patchwork)
library(Biostrings)
```
